%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 表題  2 次元非静力学モデル -- 数理モデル  参考文献
%
% 履歴  2003-07-25 高橋 こう子   新規作成
%       2004-07-25 小高正嗣      2 次元乾燥大気版へ再構成
%       2005-04-13 小高正嗣      jreport 変更, latex2html へ対応
%       2007-06-05 小高正嗣
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{参考文献}

\begin{description}
  \item 浅井 富雄, 1983: 大気対流の科学, 
        気象学のプロムナード 14, 東京堂出版.

  \item Browning, K. A., 1964: Airflow and percipitation
	within severe local storms which travel to the right
        of the winds.
        {\it J. Atmos. Sci.}, {\bf 21}, 634-639

  \item  Curic, M., Janc, D., Vujovic, D., Vuckovic, V., 2003:
	 The effects fo a river valley on an isolated
         cumulonimbus cloud development.
	 {\it Atmos. Res.}, {\bf 66}, 123-139.

  \item Das, P., 1969:
	The thermodynamic equation in cumulus dynamics.
        {\it J. Atmos. Sci.}, {\bf 26}, 399-409.

  \item Deardorff, J. W., 1975:
	The development of boundary-layer turbulence models
	for use in studying the severe storm environment.
	{\it Proc. SESAME Meeting}, Boulder, NOAA-ERL, 251-261.

  \item Houze, R. A., 1993:
        Cloud dynamics.
        Academic Press.

  \item	Kessler, E., 1969:
	On the Distribution and Continuity of Water Substance
	in Atmospheric Circuration. Meteor. Monogr.,
	{\it Amer. Meteor.Soc.}, {\bf 32}, 84 pp.

  \item Klemp J. B. and Robert B. Wilhelmson, 1978:
	The simulation of three-dimensional convective storm
	dynamics.
	{\it J. Atmos. Sci.}, {\bf 35}, 1070-1096.

  \item Klemp J. B., 1978:
	A splitting procedure for numerical solution of
	the compressible equations of motion.
	???, ???.

 \item  Marshall, J. and W. Palmer, 1948:
        The distribution of raindrops with size.
        {\it J. Meteorol.}, {\bf 5}, 165--166.

  \item Mellor, G. L., 1973:
        Analytic prediction of the properties of stratified planetary
        surface layers.
        {\it J. Atmos. Sci.}, {\bf 30}, 1061-1069.

  \item Mellor, G., and T. Yamada, 1974:
	A hierarchy of turbulence closure models for atmospheric
	boundary layers.
	{\it J. Atmos. Sci.}, {\bf 31}, 1791-1806.

  \item 中野満寿男, 2003:
        鉛直シアーが台風初期渦形成に及ぼす影響.
	九州大学大学院理学府 地球惑星科学専攻 修士論文.

  \item	Ogura, Y. and M. Yoshizaki, 1988:
	Numerical study of orographic-convective precipitation
	over the eastern Arabic Sea and the Ghats Mountains
	during the summer monsoon.
	{\it J. Atoms. Sci.}, {\bf 45}, 2097-2122.

  \item	Ogura, Y., and T. Takahashi, 1971:
	Numerical simulation of the life cycle of a thunderstorm
	cell.
	{\it Mon. Wea. Rev.}, {\bf 99}, 895-911.

  \item 大宮司久明, 三宅裕, 吉澤徴, 1998:
	乱流の数値流体力学---モデルと計算法.
	東京大学出版会, 652.

  \item	斉藤和雄 編, 1999: 非静力学モデル.
	気象研究ノート 第 196 号, 日本気象学会.

  \item Saunders, P. M., 1957:
        The thermodynamics of saturated air:
        A contribution to the classical theory.
        {\it Ouart. J. Roy. Meteor. Soc.}, {\bf 83}, 342-350.

  \item Schemm, C. E., and F. Lipps, 1976:
        Some results from a simplified three-dimensional
	numerical model of atmospheric turbulence.
        {\it J. Atmos. Sci.}, {\bf 33}, 1021-1041.

  \item Skamarock, Wiliam C. and Joseph B. Klemp, 1992:
        The stability of time-split methods for the hydrostatic
        and the nonhydrostatic elastic equation.
        {\it Mon. Wea. Rev.}, {\bf 120}, 2109-2127.

  \item Soong, S-T., and Y. Ogura, 1973:
	A comparison between axi-symmetric and slab-symmetric
	cumulus cloud models.
	{\it J. Atmos. Sci.}, {\bf 30}, 879-893

  \item Tapp, M. C., and P. W. White, 1976:
        A nonhydrostatic mesoscale model.
        {\it Quart. J. Roy. Meteor. Soc.}, {\bf 102}, 277-296.

  \item 坪木和久, 榊原篤志, 2001: CReSS ユーザーズガイド 第 2 版. \\
	\htmladdnormallink{
        http://www.tokyo.rist.or.jp/CReSS\_Fujin/CReSS.top.html}
	{http://www.tokyo.rist.or.jp/CReSS_Fujin/CReSS.top.html}

  \item Wilhelmson, R. B., 1977:
        On the thermodyanmics equation for deep convetion.
        {\it Mon. Wea. Rev.}, {\bf 105}, 545-547.

  \item Wilhelmson, R. B., and Y. Ogura, 1977:
        The pressure perturbation and the numerical modleing of
	a cloud.
        {\it J. Atmos. Sci.}, {\bf 29}, 1295-1307.
\end{description}

